Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-10 doc/main_jfm.tex
edited another paragraph in the conclusions

\todo[inline]{Bryan left off here}
Results of two JP vesicles suspended in both shear and extensional flows
have outstanding agreements with ones generated using continuum modeling
in streamlines comparisons. For two JP vesicles in shear flow, a
demonstration of rotating behavior is presented and two overlapping
trajectories of two centroid are observed as expected when two starting
centroids are placed on the same horizontal level. The hydrophobic
action and the repulsive potential lead to an adhesive effect when two
JP bilayers are within a short distance. We provide a series of results
when two JP vesicles are suspended in extensional flow. We obtain
similar results to the ones in \cite{qua-vee-you2019} when the reduced
area $A^*$ is high and both centroids are placed with some vertical
displacements.

Our future goal is to extend the current framework to a
three-dimensional JP vesicle system. The further implementation of
adding a fast algorithms such as the fast multipole method is also a
practical approach. One ongoing work is to add thermal fluctuations onto
Janus particles to obtain Brownian dynamics is crucial for obtaining
membrane diffusion. Having a more physical boundary conditions on JP
boundaries with experimental data is a reasonable direction and the
future comparison with the laboratory experiments can be accomplished.

>>>>

We compare two JP vesicles with a similar setup using a continuum model.
A comparison of the vesicle shapes and the streamlines demonstrate
remarkable similarities. The two overlapping trajectories of the JP
vesicles' centroids in a shear flow evolve as expected when the two
centroids are initialized on the same horizontal level. We also observe
a rotating behavior that is observed for models involving vesicle
adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and the
repulsive potential lead to this adhesive effect when two JP bilayers
are within a short distance. We also perform four simulations of two JP
vesicles suspended in an extensional flow. We vary the initial vertical
displacement of the vesicles' centroids and obtain similar results to
the continuum model.

\todo[inline]{Bryan left off here}
Our future goal is to extend the current framework to a
three-dimensional JP vesicle system. The further implementation of
adding a fast algorithms such as the fast multipole method is also a
practical approach. One ongoing work is to add thermal fluctuations onto
Janus particles to obtain Brownian dynamics is crucial for obtaining
membrane diffusion. Having a more physical boundary conditions on JP
boundaries with experimental data is a reasonable direction and the
future comparison with the laboratory experiments can be accomplished.
